A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Nixing TODO.

SPINN is inspired by the shift-reduce parsing formalism \citep{aho1972theory}, which builds a tree structure over a sequence (e.g., a natural language sentence) by a single left-to-right scan over its tokens. Shift-reduce parsing is frequently used in natural language parsing \citep[e.g.,][]{nivre2003efficient}.

@@

The tree-sequence hybrid models seem to be especially effective at comparing sentences with very different structures, where it is useful to use strict compositionality with the tree-structured component to get the meanings of the sentence parts, but then to also accumulate a broad sentence summary that abstracts away from the precise structures. For example, this pair is classified correctly by both hybrid models, but not by the RNN or the SPINN-PI-NT: \todo{Lexical ambiguity example/comment.}

@@

%    \subsubsection*{Acknowledgments} 
%    
%    Some of the Tesla K40(s) used for this research was/were donated by the NVIDIA Corporation.
%    \todo{[CM,CP] Acknowledge other grants.}

>>>>

SPINN is inspired by the shift-reduce parsing formalism \citep{aho1972theory}, which builds a tree structure over a sequence (e.g., a natural language sentence) by a single left-to-right scan over its tokens. Shift-reduce parsing is frequently used in natural language parsing \citep[e.g.,][]{shieber:1983:ACL,nivre2003efficient}.

@@

The tree-sequence hybrid models seem to be especially effective at comparing sentences with very different structures, where it is useful to use strict compositionality with the tree-structured component to get the meanings of the sentence parts, but then to also accumulate a broad sentence summary that abstracts away from the precise structures. For example, this pair is classified correctly by both hybrid models, but not by the RNN or the SPINN-PI-NT:

@@

%    \subsubsection*{Acknowledgments} 
%    
%    We acknowledge financial support from a Google Faculty Research Award, the Stanford Data Science Initiative, and the National Science Foundation under grant no.~BCS 1456077. Some of the Tesla K40s used for this research were donated by the NVIDIA Corporation.
